### 2011-05-10 paper.tex
Added some definitions

\newcommand{\bp}{\textsf{BP}}
\newcommand{\strongbp}{\widehat{\textsf{BP}}}
%\newcommand{\strongbp}{\textsf{strongBP}}
\newcommand{\parity}{\oplus}
\newcommand{\p}{\textsf{P}}
\newcommand{\op}{\textsf{Op}}
\newcommand{\pp}{\textsf{PP}}
\newcommand{\intersection}{\textsf{intersect}}
\newcommand{\intersect}{\textsf{intersect}}
\newcommand{\majority}{\textsf{majority}}

@@

>>>>

\newcommand{\bp}{\textsf{BP}}
\newcommand{\strongbp}{\widehat{\textsf{BP}}}
%\newcommand{\strongbp}{\textsf{strongBP}}
\newcommand{\bpp}{\textsf{BPP}}
\newcommand{\parity}{\oplus}
\newcommand{\p}{\textsf{P}}
\newcommand{\op}{\textsf{Op}}
\newcommand{\pp}{\textsf{PP}}
\newcommand{\x}{\textsf{X}}
\newcommand{\intersection}{\textsf{intersect}}
\newcommand{\intersect}{\textsf{intersect}}
\newcommand{\majority}{\textsf{majority}}

@@

\subsection{Partial Functions}

Complexity classes are usually defined in terms of \emph{languages}. A language $L$ is a subset of $\bigcup_{n=0}^{\infty}\{0,1\}^n$, which can also be viewed as a function $f_L: \bigcup_{n=0}^{\infty}\{0,1\}^n \to \{0,1\}$, where $f_L(x) = 1$ if and only if $x \in L$. However, the definitions of some complexity classes in terms of languages leads to undesirable consequences. For example, the standard definition of $\bpp$ means that a ``$\bpp$-machine'' must accept \emph{every} input with probability outside the range $[\frac{1}{3},\frac{2}{3}]$, but nearly every natural problem whose solution is described as a $\bpp$ algorithm in fact has a promise associated. The concept of a partial function is a natural way to resolve this issue.

\begin{definition}\label{partialfunction}
A \emph{partial function} is a function $f: \bigcup_{n=0}^{\infty}\{0,1\}^n \to \{0,1,\x\}$.
\end{definition}

\subsection{Complexity Classes}

For the entirety of this paper, we will use the following definitions of a complexity class and $\p$.

\begin{definition}\label{complexityclass}
A \emph{complexity class} is a set of partial functions.
\end{definition}

\begin{definition}\label{p}
The complexity class $\p$ is the set of partial functions such that $f \in \p$ if and only if there exists a polynomial $p$ and a Turing machine $T$ such that:
\begin{itemize}
\item If $f(x) = 1$, then $T$ halts after at most $p(|x|)$ steps and accepts.
\item If $f(x) = 0$, then $T$ halts after at most $p(|x|)$ steps and rejects.
\end{itemize}
\end{definition}

Notice that there is no restriction on $T$ if $f(x) = \x$. However, this definition of $\p$ can be reconciled with the standard definition of $\p$ in the following way.

\begin{remark}
For every partial function $f \in \p$, there exists another partial function $L \in \p$ such that
\begin{itemize}
\item For all $x$, $L(x) = 0$ or $L(x) = 1$.
\item If $f(x) = 1$, then $L(x) = 1$.
\item If $f(x) = 0$, then $L(x) = 0$.
\end{itemize}
\end{remark}

To see this, consider simulating $T$ and cutting it off after $p(|x|)$ steps, which is followed by a rejection. In this statement, we can see $L$ as a language in the standard complexity class $\p$, so effectively any partial function can be extended to a language.

\subsection{Operators}
